D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-17 ootavacuous.tex
Add Alan Stern's invented-load litmus tests
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Alan Stern December 17 feedback
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Listing~\ref{lst:Causality Test Case 5}
shows causality test case 5, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The \co{herd7} tool finds this OOTA cycle because C++ does not respect
data dependencies, and flags it as such using \co{S8}.
Interestingly enough, there is no state with \co{r3} also shown as
\co{S8}, perhaps indicating that \co{herd7} does not propagate OOTA
values.

@@

@@

>>>>

Listing~\ref{lst:Causality Test Case 5}
shows causality test case 5, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The \co{herd7} tool finds this OOTA cycle because C++ does not respect
data dependencies, and flags it as such using \co{S8}.

@@

\co{P1()} has a straightforward semantic dependency between its
relaxed atomic load and relaxed atomic store.
However, suppose that \co{P0()}'s load from \co{x} on line~8 returns
the value 42.
In that case, the second load on line~11 can be fused with the first,
so that it also returns the value 42.
On the other hand, if the load on line~8 returns some other value, then
line~10 will store the value 42 to \co{x}, and then the load on line~11
can be elided\footnote{
	In C++, but not in C due to atomics being volatile.}
in favor of using the value 42 stored by line~10.

Either way, the value of \co{r1} will be the constant 42.
Therefore, the loads from \co{x} cannot affect the store on line~17,
so there is no semantic dependency.
This allows that store to \co{y} to be moved to the very beginning of
\co{P0()}, thus allowing a correct real-world C++ implementation to
satisfy the \co{exists} clause.

@@

\subsubsection{Inventing Atomic Loads}
\label{app:Inventing Atomic Loads}

Listing~\ref{lst:Inventing Atomic Loads}
and~\ref{lst:Atomic Loads Invented}
shows a TBD point about inventing atomic loads.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-invented-load.litmus @@
\caption{Inventing Atomic Loads}
\label{lst:Inventing Atomic Loads}
\end{listing}

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-load-invented.litmus @@
\caption{Atomic Loads Invented}
\label{lst:Atomic Loads Invented}
\end{listing}
